Deliminative verbal reduplication in Mandarin Chinese

### 2024-09-30 replies-reviews.tex

%%%%%%%%%%%%%%%%
\noindent
\textbf{Answer:}
\citet{Xie2020} identifies the AABB form as morphological verb reduplication.
Even though we do not agree with \citegen{Xie2020} claim that the distinction between ABAB and AABB lies in the distinction between morphology and syntax,
we do agree that they are different grammatical processes and thus requires separate analyses (See also \citealt[Sec. 4.3]{Deng2013}, \citealt{Wang2023}).
Also note that there are numerous scholars that do consider the forms analyzed here as morphological processes (\citealt[Ch. 4]{Chao1968}, \citealt[Ch. 3]{LiThompson1981}, \citealt[4--5]{Liao2014} and \citealt[Sec. 4]{Sui2018}).
\citet[14--15]{Zhang2000} argues that the AABB form of reduplication develops from a completely separate historical origin from the AA and ABAB forms,
as the former has a intensifying rather than delimitative meaning.
\citet[83--84]{Xie2020} further points out that AABB is much less productive than ABAB.
This suggests that at least some AABB might not be formulated by rules but is stored in the lexicon as a whole.
This is probably the case for those AABBs that have an idiomatic meaning, such as \obj{zhi3-zhi3-dian3-dian3} `point-point-gesture-gesture, gossip'.
%Productively formed AABBs can be accounted for by the current analysis as the reduplication happens before the compounding process,
%i.e. monosyllabic verbs are reduplicated separately (as AA and BB respectively) and then compounded together to form AABB.
%This is in line with the proposal in \citet[Sec. 4.2]{Wang2023},
%and also explains why some AABBs do not have a base AB form, such as \textit{zou-zou-ting-ting} `walk-walk-stop-stop, walk for a while and rest for a while', *\textit{zou-ting} `walk-stop'
The current analysis has a broad scope in that it explains all forms of delimitative verbal reduplication, which previous analyses were not able to do.
An analysis for the AABB form of reduplication has to be left for further research.

Note that technically accounting for AABB under current assumptions is not difficult. The phonology
can be split into two parts A and B and be combined to yield AABB in the output of a lexical
rule. What has to be examined carefully in future work
is the empirical domain of these reduplications.

% \itdopt{St. Mü: Können wir das nicht auch AABB? Das ist gar nicht schwer. Ich habe das für
%   adverbiale Adjektive bereits implementiert. Man muss nur PHON in zwei Teile \ibox{1} und \ibox{2}
%   spalten und dann eben \ibox{1} $\oplus$ \ibox{1} $\oplus$ \ibox{2} $\oplus$ \ibox{2} als PHON-Wert
% nehmen. Wenn das wichtig ist, können wir das noch machen. Oder wir machen eine Fußnote hin.}

@@

%%%%%%%%%%%%%%%%%%%%
\noindent
\textbf{Answer}:
It is not \obj{san1} \obj{xia4} `three times' that is special, but it is \obj{yi2} \obj{xia4} `once' that is special.
We can replace \obj{san1} `three' with any number above two,
and the distinction still exist.
But \obj{yi2} \obj{xia4} `once' has acquired a duration reading `for a little while' that is not available to the other event quantifiers formed by \obj{xia4}, which only have the `for X times' interpretation (\citealt[77]{Deng2013}, \citealt[16]{Zhang2000}).
We think \obj{liang3} \obj{xia4} `twice' is following this tendency, too.
In this case, it is easy to interpret \obj{yi1} \obj{xia4} and \obj{liang3} \obj{xia4} not as referring to the actual number of action taking place,
but as duration adverbials as a whole,
thus differing them from ``actual'' verbal classifier phrases with other numerals.
%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%
%% Stefan
\item
\begin{displayquote}
R2 comments on the following passage: They provided
22 the lexical rule (48) for reduplication in general, and further proposed \textit{redup-a-lr} and \textit{redup-v-lr} as subtypes of redup-type, as illustrated in (49) and (50) respectively.
\end{displayquote}

It would enhance reader comprehension if the authors could provide a brief illustration of symbols
like HOOK, LTOP, IND, ARG, etc. This will aid readers in better grasping the authors' subsequent
proposals in Section 4.

\textbf{Answer:}\label{ltop}
We added a footnote about \textsc{hook} and explained \textsc{ltop}, \textsc{ind} and \textsc{arg}
in the analysis section.

### 2024-09-30 chapters/ch05-Analysis.tex
AABB comment, features ARG0-3 erklärt

Like \citet{FanSongBond2015}, we assume lexical rules for reduplication. Our lexical rules are
organized in an inheritance network. \textit{verbal-reduplication-lr} is the most general type for
reduplication lexical rules in this network and the implicational constraint in (\ref{avm:redup}) shows the constraints on all
structures of type \textit{verbal-reduplication-lr}. Such structures take a verb as
\textsc{lexical-daughter (lex-dtr)}.  The output reduplicates the \textsc{phonology (phon)} of the
input verb with the possibility to have further phonological material in between.  \etag{} indicates
an underspecified list which could be empty or not.\footnote{%
The \etag is equivalent to a tag with a number with the difference that \etag is never shared. We
follow Müller (\citeyear[161]{Mueller2002b}, \citeyear[294]{Mueller2003e}) and elsewhere in using this
notation, since we think this is more
precise than simply using three dots.}
A delimitative relation is appended to the
\textsc{relations (rels)} value of the input verb, and it takes the event index of the input verb \iboxb{3} as
argument. The list of relations contains so-called elementary predications. There is no complicated
embedding of relations. Instead each elementary predication comes with a label (\textsc{lbl}). The
label can be used as an argument of another relation or in scope constraints, which are not provided
here to keep things simple. The feature \textsc{ltop} points to the local top. This is the
elementary predication that is considered the top-most one in the \relsl. Other elementary
predications may share the label or have arguments with labels of other elementary predications. We
will discuss an example below when we discuss the perfective lexical rule.
The label of the output \iboxb{2} is identified with the label of the input and with the
label of the delimitative relation, hence \type{delimitative-rel} is treated as a modifier.  Further
relations can be added at the beginning of the \textsc{rels} list to allow for the additional
perfective meaning in A-\textit{le}-A and A-\textit{le}-\textit{yi}-A.  The combination with the
perfective will be elaborated on in the following paragraphs.

>>>>

Like \citet{FanSongBond2015}, we assume lexical rules for reduplication. Our lexical rules are
organized in an inheritance network. \textit{verbal-reduplication-lr} is the most general type for
reduplication lexical rules in this network and the implicational constraint in (\ref{avm:redup}) shows the constraints on all
structures of type \textit{verbal-reduplication-lr}. Such structures take a verb as
\textsc{lexical-daughter (lex-dtr)}.  The output reduplicates the \textsc{phonology (phon)} of the
input verb with the possibility to have further phonological material in between.  \etag{} indicates
an underspecified list which could be empty or not.\footnote{%
The \etag is equivalent to a tag with a number with the difference that \etag is never shared. We
follow Müller (\citeyear[161]{Mueller2002b}, \citeyear[294]{Mueller2003e}) and elsewhere in using this
notation, since we think this is more
precise than simply using three dots.}
A delimitative relation is appended to the
\textsc{relations (rels)} value of the input verb, and it takes the event index of the input verb \iboxb{3} as
argument (\textsc{arg0}, \ldots, \textsc{arg3} are feature names for arguments. The values are
indices or events similar to variables in normal predicate logic.). The list of relations contains so-called elementary predications. There is no complicated
embedding of relations. Instead each elementary predication comes with a label (\textsc{lbl}). The
label can be used as an argument of another relation or in scope constraints, which are not provided
here to keep things simple. The feature \textsc{ltop} points to the local top. This is the
elementary predication that is considered the top-most one in the \relsl. Other elementary
predications may share the label or have arguments with labels of other elementary predications. We
will discuss an example below when we discuss the perfective lexical rule.
The label of the output \iboxb{2} is identified with the label of the input and with the
label of the delimitative relation, hence \type{delimitative-rel} is treated as a modifier.  Further
relations can be added at the beginning of the \textsc{rels} list to allow for the additional
perfective meaning in A-\textit{le}-A and A-\textit{le}-\textit{yi}-A.  The combination with the
perfective will be elaborated on in the following paragraphs.
